---
title: "Assignment 2 - Analysis"
format: html
---

## Task 3: Setup

```{r}
#| message: false
#| warning: false
library(dplyr)
library(readr)
```

## Task 4: Load Data

```{r}
nhanes <- read_csv("examples/nhanes-equity/data/nhanes_equity_v6.csv", show_col_types = FALSE)
# getwd() 
```

## Task 5: Inspect
> Inspect the dataset with row count, column names, variable types, and missingness.

```{r}
nrow(nhanes)
```
```{r}
names(nhanes)
```
```{r}
glimpse(nhanes)
```
```{r}
colSums(is.na(nhanes))
```

## Task 6: Summarize Table
> Create one cleaned or analysis-ready table using at least three dplyr verbs.
```{r}
bmi_summary <- nhanes |>
  select(BMI, Gender, IncomeGroup) |>
  filter(!is.na(Gender) & !is.na(BMI) & !is.na(IncomeGroup)) |>
  group_by(IncomeGroup, Gender) |>
  summarise(
    n = n(),
    mean_bmi = mean(BMI),
    .groups = "drop"
  )

bmi_summary
```

## Task 7: Function
> Write one custom function, such as a function that returns mean and SD for a numeric variable.

```{r}
mean_with_sd <- function(x) {
  tibble(mean = mean(x, na.rm = TRUE),
           sd = sd(x, na.rm = TRUE))
}
mean_with_sd(nhanes$BMI)
```

## Save Output

```{r}
dir.create("assignments/assignment02-r-with-ai/submission/output", recursive = TRUE, showWarnings = FALSE)
write_csv(bmi_summary, "assignments/assignment02-r-with-ai/submission/output/summary_table.csv")
```

## AI Audit Note
AI was not used for this submission.
